% add \usepackage{seqsplit} to your preamble 
\seqsplit{OntOvertopping:AngleOfDownSlope~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:AngleOfUpperSlope~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:AngleOfWaveAttack~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:ArmourFreeboardRelativeToSWL~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:ArmourWidth~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:BermSlope~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:BermWidth~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:CrestFreeboardRelativeToSWL~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:DerivedQuantity~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntOvertopping:InputParameter~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntOvertopping:MeanOvertoppingDischarge~{$\sqsubseteq$}~OntOvertopping:DerivedQuantity} \\
\seqsplit{OntOvertopping:MeanOvertoppingDischarge~{$\sqsubseteq$}~OntOvertopping:OutputParameter} \\
\seqsplit{OntOvertopping:NN\_Overtopping2~{$\sqsubseteq$}~OntOvertopping:OvertoppingForecastModel} \\
\seqsplit{OntOvertopping:OutputParameter~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntOvertopping:RoughnessCoefficient~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:SignificantWaveHeight~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:WaterDepthAtToeOfBreakwater~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:WaterDepthAtToeOfBreakwater~{$\sqsubseteq$}~OntOvertopping:WaveCondition} \\
\seqsplit{OntOvertopping:WaterDepthInFrontOfStructure~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:WaterDepthOnBerm~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:WaveAngle~{$\sqsubseteq$}~OntOvertopping:WaveCondition} \\
\seqsplit{OntOvertopping:WaveCondition~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntOvertopping:WaveDirection~{$\sqsubseteq$}~OntOvertopping:WaveCondition} \\
\seqsplit{OntOvertopping:WavePeriod~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:WavePeriod~{$\sqsubseteq$}~OntOvertopping:WaveCondition} \\
\seqsplit{OntOvertopping:WidthOfToe~{$\sqsubseteq$}~OntOvertopping:InputParameter} \\
\seqsplit{OntOvertopping:hasOvertoppingInputParameter~{$\sqsubseteq$}~OntOvertopping:hasInputParameter} \\
\seqsplit{OntOvertopping:hasOvertoppingOutputParameter~{$\sqsubseteq$}~OntOvertopping:hasOutputParameter} \\
\seqsplit{{$\exists$}~om:hasUnit.{$\top$}~{$\sqsubseteq$}~om:Measure} \\
\seqsplit{{$\exists$}~om:hasValue.{$\top$}~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{{$\exists$}~OntOvertopping:attacks.{$\top$}~{$\sqsubseteq$}~OntOvertopping:Wave} \\
\seqsplit{{$\exists$}~OntOvertopping:generates.{$\top$}~{$\sqsubseteq$}~OntOvertopping:OvertoppingForecastModel} \\
\seqsplit{{$\exists$}~OntOvertopping:hasAttackAngle.{$\top$}~{$\sqsubseteq$}~OntOvertopping:Wave} \\
\seqsplit{{$\exists$}~OntOvertopping:hasInputParameter.{$\top$}~{$\sqsubseteq$}~OntOvertopping:OvertoppingForecastModel} \\
\seqsplit{{$\exists$}~OntOvertopping:hasOutputParameter.{$\top$}~{$\sqsubseteq$}~OntOvertopping:OvertoppingForecastModel} \\
\seqsplit{{$\exists$}~OntOvertopping:hasOvertoppingInputParameter.{$\top$}~{$\sqsubseteq$}~OntOvertopping:NN\_Overtopping2} \\
\seqsplit{{$\exists$}~OntOvertopping:hasOvertoppingOutputParameter.{$\top$}~{$\sqsubseteq$}~OntOvertopping:NN\_Overtopping2} \\
\seqsplit{{$\exists$}~OntOvertopping:hasPart.{$\top$}~{$\sqsubseteq$}~OntOvertopping:CoastalDefenceStructure} \\
\seqsplit{{$\exists$}~OntOvertopping:hasWaveCondition.{$\top$}~{$\sqsubseteq$}~OntOvertopping:Wave} \\
\seqsplit{{$\exists$}~OntOvertopping:isMeasuredAgainst.{$\top$}~{$\sqsubseteq$}~OntOvertopping:AngleOfWaveAttack} \\
\seqsplit{{$\exists$}~OntOvertopping:managesForecastOf.{$\top$}~{$\sqsubseteq$}~OntOvertopping:OvertoppingForecast} \\
\seqsplit{{$\exists$}~OntOvertopping:measuredAt.{$\top$}~{$\sqsubseteq$}~OntOvertopping:MeanOvertoppingDischarge} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasUnit.om:Unit} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasValue.om:Measure} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:attacks.OntOvertopping:CoastalDefenceStructure} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:generates.OntOvertopping:OvertoppingForecast} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasAttackAngle.OntOvertopping:AngleOfWaveAttack} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasInputParameter.OntOvertopping:InputParameter} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasOutputParameter.OntOvertopping:OutputParameter} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasOvertoppingInputParameter.(OntOvertopping:AngleOfDownSlope~{$\sqcup$}~OntOvertopping:AngleOfUpperSlope~{$\sqcup$}~OntOvertopping:AngleOfWaveAttack~{$\sqcup$}~OntOvertopping:ArmourFreeboardRelativeToSWL~{$\sqcup$}~OntOvertopping:ArmourWidth~{$\sqcup$}~OntOvertopping:BermSlope~{$\sqcup$}~OntOvertopping:BermWidth~{$\sqcup$}~OntOvertopping:CrestFreeboardRelativeToSWL~{$\sqcup$}~OntOvertopping:RoughnessCoefficient~{$\sqcup$}~OntOvertopping:SignificantWaveHeight~{$\sqcup$}~OntOvertopping:WaterDepthAtToeOfBreakwater~{$\sqcup$}~OntOvertopping:WaterDepthInFrontOfStructure~{$\sqcup$}~OntOvertopping:WaterDepthOnBerm~{$\sqcup$}~OntOvertopping:WavePeriod~{$\sqcup$}~OntOvertopping:WidthOfToe)} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasOvertoppingOutputParameter.OntOvertopping:MeanOvertoppingDischarge} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasPart.OntOvertopping:CrestWall} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:hasWaveCondition.OntOvertopping:WaveCondition} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:isMeasuredAgainst.OntOvertopping:CrestWall} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:managesForecastOf.OntOvertopping:Overtopping} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntOvertopping:measuredAt.OntOvertopping:CrestWall} \\
\seqsplit{{$\exists$}~om:hasNumericalValue.{$\top$}~{$\sqsubseteq$}~om:Measure} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasNumericalValue.xsd:float} \\
